Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-04 testbed.tex
more testbed

@@

Call set\_hostname script at startup. We insert a line of code to call script in rc.local just after the initial comments (i.e. lines starting with \#).
\begin{lstlisting}[]
# line_number=$(egrep -n -m1 "(^[^#])|(^$)" ${ROOTDIR}/etc/rc.local | cut -d: -f1)
# sed -i "${line_number}c bash /home/pi/rasp_config/set_hostname" ${ROOTDIR}/etc/rc.local
\end{lstlisting}
\FloatBarrier
%$ line="bash /home/pi/.rasp_config/set_hostname"
%# awk -v text="$line" '!/^#/ && !p {print text; p=1} 1' ${ROOTDIR}/etc/rc.local > <@ \Suppressnumber @>
%    ${ROOTDIR}/etc/rc.local <@ \Reactivatenumber @>

All other files could be updated.

@@

It may be desired to pre-install some programs in the image before it is
written to all the memory cards that goes into the Raspberry pis.
This can be done using QEMU Chroot (change root).
\url{https://wiki.archlinux.org/index.php/Raspberry_Pi}

\fxnote{Lets use RPi for Raspberry Pis throughout the paper!}
\fxnote{Which packages is required for this on debian/ubuntu?}

>>>>

We have packed the files and uploaded them to a webserver. These can be
retrieved with wget and unziped into the Raspbian lite image that
we are customizing:

@@

"nodes.csv" can be changed using a text editor. For vim, this could be done
the following way:
\begin{lstlisting}[]
# vim ${ROOTDIR}/home/pi/rasp_config/nodes.csv
\end{lstlisting}
\FloatBarrier

Finally, to actually make the \ac{Raspi}s change hostname, we have to make
each \ac{Raspi} call the above script when it starts up.
Do this by inserting the line below in "\$\{ROOTDIR\}/etc/rc.local".
The file
can be opened with your favorite text editor.

\begin{lstlisting}[]
bash /home/pi/rasp_config/set_hostname"
\end{lstlisting}
\FloatBarrier

%This can be done by inserting a call to the script
%set\_hostname in rc.local before it exits.
%
%Call set\_hostname script at startup. We insert a line of code to call script in rc.local just after the initial comments (i.e. lines starting with \#).
%\begin{lstlisting}[]
%# line_number=$(egrep -n -m1 "(^[^#])|(^$)" ${ROOTDIR}/etc/rc.local | cut -d: -f1)
%# sed -i "${line_number}c bash /home/pi/rasp_config/set_hostname" ${ROOTDIR}/etc/rc.local
%\end{lstlisting}
%\FloatBarrier
%$ line="bash /home/pi/.rasp_config/set_hostname"
%# awk -v text="$line" '!/^#/ && !p {print text; p=1} 1' ${ROOTDIR}/etc/rc.local > <@ \Suppressnumber @>
%    ${ROOTDIR}/etc/rc.local <@ \Reactivatenumber @>

All other files could be updated as well.

@@

It may be desired to pre-install some programs in the image before it is
written to all the memory cards that goes into the \ac{Raspi}s.
This can be done using QEMU Chroot (change root).
\url{https://wiki.archlinux.org/index.php/Raspberry_Pi}

\fxnote{Which packages is required for this on debian/ubuntu?}
